Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
verbal adverbs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60944 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{figure}[htbp]
	\centering
	\begin{dependency}[theme = simple, font = \small]
		\begin{deptext}[column sep=0.08cm]
			Бразилия \& өз \& жерінде \& чемпионатты \& екі \& рет \& өткізген \& бесінші \& ел \& болды. \\
			\gmk{np.nom} \& \gmk{det} \& \gmk{nom.px3sp.loc} \& \gmk{n.acc} \& \gmk{num} \& \gmk{n} \& \gmk{v.tv.gpr} \& \gmk{num.ord} \& \gmk{n.nom} \& \gmk{v.iv.ifi} \\
			\tgloss{Brasil} \& \tgloss{own} \& \tgloss{in its land} \& \tgloss{championship} \& \tgloss{two} \& \tgloss{times} \& \tgloss{having held} \& \tgloss{fifth} \& \tgloss{country} \& \tgloss{became} \\
		\end{deptext}
		\depedge{3}{2}{\udlabel{det}}
		\depedge{7}{3}{\udlabel{nmod}}
		\depedge{7}{4}{\udlabel{obj}}
		\depedge{6}{5}{\udlabel{nummod}}
		\depedge{7}{6}{\udlabel{nmod}}
		\depedge{9}{7}{\udlabel{acl}}
		\deproot[edge unit distance=1.3ex]{9}{\udlabel{root}}
	\end{dependency}
	\caption{Verbal adjectives: verbal adjectives are the head of everything in their own clause and are an \udtag{acl} dependency of the noun they modify.}\label{fig:gpr}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\begin{dependency}[theme = simple, font = \small]
		\begin{deptext}[column sep=0.08cm]
			Бразилия \& өз \& жерінде \& чемпионатты \& екі \& рет \& өткізген \& бесінші \& ел \& болды. \\
			\gmk{np.nom} \& \gmk{det} \& \gmk{nom.px3sp.loc} \& \gmk{n.acc} \& \gmk{num} \& \gmk{n} \& \gmk{v.tv.gpr} \& \gmk{num.ord} \& \gmk{n.nom} \& \gmk{v.iv.ifi} \\
			\tgloss{Brasil} \& \tgloss{own} \& \tgloss{in its land} \& \tgloss{championship} \& \tgloss{two} \& \tgloss{times} \& \tgloss{having held} \& \tgloss{fifth} \& \tgloss{country} \& \tgloss{became} \\
		\end{deptext}
		\depedge{3}{2}{\udlabel{det}}
		\depedge{7}{3}{\udlabel{nmod}}
		\depedge{7}{4}{\udlabel{obj}}
		\depedge{6}{5}{\udlabel{nummod}}
		\depedge{7}{6}{\udlabel{nmod}}
		\depedge{9}{7}{\udlabel{acl}}
		\depedge{9}{8}{\udlabel{amod}}
		\depedge{9}{10}{\udlabel{cop}}
		\deproot[edge unit distance=1.3ex]{9}{\udlabel{root}}
	\end{dependency}
	\caption{Verbal adjectives: verbal adjectives are the head of everything in their own clause and are an \udtag{acl} dependency of the noun they modify.}\label{fig:gpr}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{dependency}[theme = simple, font = \small]
		\begin{deptext}[column sep=0.08cm]
			1960 \& жылдан \& бастап \& Батыс \& үлгісінде \& дами \& бастады. \\
			\gmk{num} \& \gmk{n.abl} \& \gmk{v.tv.gna} \& \gmk{n.nom} \& \gmk{n.px3sp.loc} \& \gmk{v.iv.prc} \& \gmk{vaux.ifi} \\
			\tgloss{1960} \& \tgloss{from year} \& \tgloss{starting} \& \tgloss{the West} \& \tgloss{on its model} \& \tgloss{developing} \& \tgloss{started} \\
		\end{deptext}
		\depedge{2}{1}{\udlabel{amod}}
		\depedge{3}{2}{\udlabel{nmod}}
		\depedge{6}{3}{\udlabel{advcl}}
		\deproot[edge unit distance=1.3ex]{6}{\udlabel{root}}
	\end{dependency}
	\caption{Verbal adverbs: verbal adverbs are the head of everything in their own clause and are an \udtag{advcl} dependency of the verb they are subordinate to.}\label{fig:gpr}
\end{figure}
